Barriers to meaningful data sharing

### 2021-04-01 new-paper.Rmd

1 = Monash University, Department of Econometrics and Business Statistics, Melbourne, Australia\\
2 = Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)\\
3 = Berkeley Institute for Data Science, University of California, Berkeley, USA\\
* = Both authors contributed equally to the work\\
Correspondence to:\\
Nicholas Tierney (nicholas.tierney@gmail.com) and Karthik Ram (karthik.ram@berkeley.edu)

>>>>

1 = Monash University, Department of Econometrics and Business Statistics, Melbourne, Australia\\
2 = Australian Centre of Excellence for Mathematical and Statistical Frontiers (ACEMS)\\
3 = Telethon Kids Institute, Perth Children's Hospital, Perth, Australia\\
4 = Berkeley Institute for Data Science, University of California, Berkeley, USA\\
* = Both authors contributed equally to the work\\
Correspondence to:\\
Nicholas Tierney (nicholas.tierney@gmail.com) and Karthik Ram (karthik.ram@berkeley.edu)
